---
title: "ACCORD GROUP - BARCELONA ESMO CONGRESS"
author: "YOUR EVENT"
date: 'SEPTEMBER 26TH TO OCTOBER 1ST 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```


## **SUGGESTED RESTAURANTS** {.tabset .tabset-fade .tabset-pills}

We have offered the following restaurants according to the group budget and also the hotel location. All restaurants are located walking distance from Hotel Catalonia Portal del Angel 


<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1CRWfos2r2Ez4cV-rkMYpOBU3U22ESk0A" width="640" height="480"></iframe>


### **RACO DE NURIA**


<iframe src="RacodeNuria.html"  frameborder="0" width="100%" height="1600" scrolling="no"></iframe>


### **AGUELO013**

<iframe src="Aguelo013/Aguelo013.html"  frameborder="0" width="100%" height="1000" scrolling="no"></iframe>

### **ARROS I PEIX**

<iframe src="Arros i Peix/ArrosiPeix.html"  frameborder="0" width="100%" height="1600" scrolling="no"></iframe>


### **CASA LOLA** 

<iframe src="Casa Lola /CasaLola.html"  frameborder="0" width="100%" height="1600" scrolling="no"></iframe>
 

### **CASA CARMEN** 

<iframe src="Casa Carmen/CasaCarmen.html"  frameborder="0" width="100%" height="1600" scrolling="no"></iframe>


### **JULIVERT MEU** 

<iframe src="Julivert Meu/Julivert.html"  frameborder="0" width="100%" height="1600" scrolling="no"></iframe>




*****

## Budget

<iframe src="https://accordgrouprestaurantsbudget.netlify.com/" width="100%" height="1000"></iframe>

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Your Events Romania
  
  * For a group of minimum 20 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
*****





